Montreal Real Estate Pricing \\ {\normalsize Code available at: \url{https://github.com/mike-n-7/ML4}}

### 2014-12-05 Paper/paper.tex
Tables added.

	Due to the fact that there was a significant amount of missing data, we investigated not only algorithm performance but also methods for treating the missing data. Each algorithm was run on the three datasets resulting from these treatments. Algorithms were optimized for better results on training sets and a held out test set was used for final evaluation.

@@

	Features consisted of two broad categories, property descriptors and integer counts of the number of instances of municipal infrastructure within walking distance from the datapoint. Many of the features were inherently numerical so they remained untouched. Categorical data such as the property type (house, condo etc...) or the year it was sold (2002-unsold) could have been encoded using integer codes. Research has shown however that one-hot encoding yields better results. [4] These two characteristics hence exploded into a set of binary features.

@@

	A closed form solution does exist but the remaining details, while interesting, are not pertinent.

@@

\subsubsection{K Nearest Neighbours}
	K nearest neighbours take a different approach. The core assumption made with this method is that examples with similar feature values should have similar outputs. Neighbours of a queried datapoint should be used to determine it's value and not points that are far away. In a regression task, once the neighbours have been located, the mean of their values (or a weighted average) is taken to assign to the queried point.

@@

\subsection{Implementation Details}
	Raw data had to be scraped from real estate websites. To do so we used the popular Scrapy framework available for python \cite{scrapy}. A spider was written for each website and data from which was loaded through a script into a cohesive raw dataset. This raw data was then cleansed by removing outliers and bad data and extended using the Montreal datasets as discussed previously. All scripts for collecting and pre-processing of data is available in the code base (though Scrapy will need to be installed in order to scrape raw data).

@@

\subsection{Training/Testing}

@@

\subsection{Linear Regression}
	Figure \ref{fig:linreg} compares the performance of Linear Regression over the three datasets representing approaches to handling missing data. Best performance was with the malformed data removed and yielded a MSE of about \$45,000.

	 \begin{figure}[!htbp]
   		\centering
  		\includegraphics[width=\linewidth]{linear_regression_tuning.png}
    		\caption{Performance of Linear Regression algorithm}
    		\label{fig:linreg}
	\end{figure}

\subsection{Lasso Regression}
	Lasso's lambda parameter was optimized but performance seemed to be only marginally affected. Figure \ref{fig:lassoreg} shows once again that removing the missing data was most fruitful. Best MSE was approximately \$44,000.

	 \begin{figure}[!htbp]
   		\centering
  		\includegraphics[width=\linewidth]{lasso_tuning_plot.png}
    		\caption{Performance of Lasso Regression algorithm}
    		\label{fig:lassoreg}
	\end{figure}

\subsection{K Nearest Neighbours}
	The optimal K was [INSERT], as shown in Figure \ref{fig:knn}. Once again simply removing the bad data yielded the best results.

	\begin{figure}[!htbp]
   		\centering
  		\includegraphics[width=\linewidth]{knn_tuning.png}
    		\caption{Performance of K-Nearest Neighbours as a function of K}
    		\label{fig:knn}
	\end{figure}

\subsection{Feature Selection}
	A major driving force of this project was to determine whether the data provided by the city of Montreal was useful in pricing homes across the island. Would the location of certain infrastructure help in the prediction of the worth of a particular property? Two of the algorithms tested above implicitly ranks the features by assigning weights to each feature dimension. The higher the magnitude of the weight, the more important it is in determining price. Figure \ref{fig:feats} shows how Linear Regression and Lasso Regression treated each of the 38 features.

>>>>

	Due to the fact that there was a significant amount of missing data, we investigated not only algorithm performance but also methods for treating the missing data. Each algorithm was run with each of the methods for handling missing data. Algorithms were optimized for better results on training sets and a held out test set was used for final evaluation. To select the best method of removing missing data and for tuning hyperparameters, 5-fold cross validation was used. When the missing data imputation required statistics from the data (EM and mean imputation), the model was generated on only the training data and then these models were used to impute the values of the test data.

@@

	Features consisted of two broad categories, property descriptors and integer counts of the number of instances of municipal infrastructure within walking distance from the datapoint. Many of the features were inherently numerical so they remained untouched. Categorical data such as the property type (house, condo etc...) or the year it was sold (2002-unsold) could have been encoded using integer codes. Research has shown however that one-hot encoding yields better results. [4] This is because there is no inherent linear relationship between each set of features and one parameter cannot capture the relationship between all the categories. These two characteristics are hence exploded into a set of binary features.

@@

	A closed form solution does exist but the remaining details, while interesting, are not pertinent. Linear regression is an algorithm of interest to us not only because it is a common method used for economic modelling, but it has an ituitive interpretation. Based on the magnitude of the weights, we can tell which parameters most influence the price of a house and whether there is a positive or negative correlation. The goal of this paper is to do exactly this.

@@

\subsubsection{K Nearest Neighbours}
	K nearest neighbours take a different approach. The core assumption made with this method is that examples with similar feature values should have similar outputs. Neighbours of a queried datapoint should be used to determine its value and not points that are far away. In a regression task, once the neighbours have been located, the mean of their values (or a weighted average) is taken to assign to the queried point.

@@

	Being a lazy learner, K nearest neighbours has a strong dependency on the actual dataset. This means the the way we come up with missing data is important as a poorly estimated value can push an otherwise close point farther away. The distance function is also of large importance to this method. By default scikit-learn uses the Euclidean distance. This may not be the best choice for the metric as discussed in the discussion.

\subsection{Implementation Details}
	Raw data had to be scraped from real estate websites. To do so we used the popular Scrapy framework available for python \cite{scrapy}. A spider was written for each website and data from each was loaded through a script into a cohesive raw dataset. This raw data was then cleansed by removing outliers and bad data and extended using the Montreal datasets as discussed previously. All scripts for collecting and pre-processing of data is available in the code base (though Scrapy will need to be installed in order to scrape raw data).

@@

@@

\subsection{Linear Regression}
	Figure \ref{fig:linreg} compares the performance of Linear Regression over the three datasets representing approaches to handling missing data. Best performance was with the malformed data removed and yielded a MSE of \$44,680 as seen in table \ref{fig:linregres}.

	 \begin{figure}[!htbp]
   		\centering
  		\includegraphics[width=\linewidth]{linear_regression_tuning.png}
    		\caption{Performance of Linear Regression algorithm}
    		\label{fig:linreg}
	\end{figure}
	\begin{center}

    \begin{table}	
    \begin{tabular}{| l | l |}
    \hline
    Missing Data Method & Mean Absolute Error \\ \hline
    \hline
    Removal & 44680 \\
    \hline
    Mean Imputation & 61335 \\
    \hline
    Expectation Maximization & 63672 \\
    \hline
    \end{tabular}
    \caption{Mean absolute error for linear regression using various methods to handle missing data.}
    \label{fig:linregres}
    \end{table}
\end{center}
\subsection{Lasso Regression}
	For lasso regression, along with testing each missing data method, we also optimized the regularization hyperparameter, $\lambda$. However, performance seemed to be only marginally affected. Figure \ref{fig:lassoreg} shows once again that removing the missing data was most fruitful. Best MSE was approximately \$44,315 using a$ \lambda$ value of 100.

	 \begin{figure}[!htbp]
   		\centering
  		\includegraphics[width=\linewidth]{lasso_tuning_plot.png}
    		\caption{Performance of Lasso Regression algorithm}
    		\label{fig:lassoreg}
	\end{figure}
	The results for optimizing each data removal method can be found in table \ref{fig:lassores}.
	\begin{center}
	\begin{table}	
    \begin{tabular}{| l | l | l |}
    \hline
    Missing Data Method & $\lambda$ & Mean Absolute Error \\ \hline
    \hline
	Removal & 0.1 & 44485 \\
	\hline
	Removal & 0.3 & 44482 \\
	\hline
	Removal & 1 & 44477 \\
	\hline
	Removal & 3 & 44469 \\
	\hline
	Removal & 10 & 44457 \\
	\hline
	Removal & 33 & 44402 \\
	\hline
	Removal & 100 & 44315 \\
	\hline
	Removal & 333 & 44373 \\
	\hline
    Mean Imputation & 0.1 & 61080\\
    \hline
 Mean Imputation & 0.3 & 61079\\
 \hline
 Mean Imputation & 1 & 61079\\
 \hline
 Mean Imputation & 3 & 61079\\
 \hline
 Mean Imputation & 10 & 61078\\
 \hline
 Mean Imputation & 33 & 61079\\
 \hline
 Mean Imputation & 100 & 61109 \\
 \hline
 Mean Imputation & 333 & 61279 \\
    \hline
    Expectation Maximization & 0.1 & 64640\\
    \hline
Expectation Maximization & 0.3 & 64640\\
\hline
Expectation Maximization & 1 & 64639\\
\hline
Expectation Maximization & 3 & 64636\\
\hline
Expectation Maximization & 10 & 64629\\
\hline
Expectation Maximization & 33 & 64645\\
\hline
Expectation Maximization & 100 & 64682\\
\hline
Expectation Maximization & 333 & 64895 \\
    \hline
    \end{tabular}
    \caption{Mean absolute error for lasso regression using various methods to handle missing data and tuning the regularization parameter.}
    \label{fig:lassores}
    \end{table}
\end{center}

\subsection{K Nearest Neighbours}
	The optimal K was 5, as shown in Figure \ref{fig:knn}. Once again simply removing the missing data yielded the best results. Complete summaries of tuning parameters can be found in table \ref{fig:knnres}.

	\begin{figure}[!htbp]
   		\centering
  		\includegraphics[width=\linewidth]{knn_tuning.png}
    		\caption{Performance of K-Nearest Neighbours as a function of K}
    		\label{fig:knn}
	\end{figure}
	\begin{center}
	\begin{table}	
    \begin{tabular}{| l | l | l |}
    \hline
    Missing Data Method & k & Mean Absolute Error \\ \hline
    \hline
	Removal & 1 & 53237 \\
	\hline
Removal & 5 & 45209\\
\hline
Removal & 10 & 45960\\
\hline
Removal & 25 & 48585\\
\hline
Removal & 50 & 52868\\
	\hline
    Mean Imputation & 1 & 78259\\
    \hline
Mean Imputation & 5& 68398\\
\hline
Mean Imputation & 10 &68553\\
\hline
Mean Imputation & 25 &71210\\
\hline
Mean Imputation & 50& 73907\\
    \hline
    Expectation Maximization & 1 & 73183\\
    \hline
Expectation Maximization & 5 &62981\\
\hline
Expectation Maximization & 10 &63364\\
\hline
Expectation Maximization & 25 &65266\\
\hline
Expectation Maximization & 50 &67519\\
    \hline
    \end{tabular}
    \caption{Mean absolute error for kNN using various methods to handle missing data and tuning the number of neighbours.}
    \label{fig:knnres}
    \end{table}
\end{center}
\subsection{Feature Selection}
	A major driving force of this project was to determine whether the data provided by the city of Montreal was useful in pricing homes across the island. Would the location of certain infrastructure help in the prediction of the worth of a particular property? Two of the algorithms tested above implicitly ranks the features by assigning weights to each feature dimension. The higher the magnitude of the weight, the more important it is in determining price. Figure \ref{fig:feats} shows how Linear Regression and Lasso Regression treated each of the 38 features.
